Panel Seminars

### 2021-05-17 index.Rmd
Updated panelists and members

Everyone is welcome to join!

@@

| Date        | Topic       | Panelists     |
| :---        | :---        | :---          |
| May 7         | GBS/RADseq genotyping pipelines     | [Melanie LaCava](https://melanielacava.weebly.com/), [Alicia Mastretta-Yanes](http://mastrettayanes-lab.org/), [Isaac Overcast](https://isaacovercast.github.io/), [Jon Puritz](https://www.marineevoeco.com/)   |
| May 21       |  WGS genotyping (low and high coverage)     | [Mikhail "Misha" Matz](https://matzlab.weebly.com/), [Tim Sackton](https://scholar.harvard.edu/tsackton), [Nina Overgaard Therkildsen](https://www.therkildsenlab.com/), TBD |
| June 4       |  Population genomic analyses and filtering data     | TBD|
| June 18       |  Functional Genomics (RNAseq)     | TBD|

# Reproducibility in Marine Genomics  
The working group is also currently hosting three undergraduate research interns with funding from the [RCN-ECS](https://rcn-ecs.github.io/). These interns are part of a sub-committee conducting a literature survey to characterize trends in data availability, code accessibility, and methods reproducibility in papers that use genomics to study adaptation in marine systems. The results of this survey will be shared in a peer-reviewed article, along with guidance to improve the state of reproducibility in the field.  
# Working Group Members

#### [Katherine Silliman, PhD](https://ksilliman.weebly.com/), Auburn University - kes0132[at]auburn.edu
#### [Sam Bogan](http://www.hofmannlab.com/sam-bogan.html), UC-Santa Barbara -snbogan[at]ucsb.edu
#### [Alan Downey-Wall](https://cos.northeastern.edu/people/alan-downey-wall/), Northeastern University 
#### Chris Mantegna, University of Washington  
#### [Danielle Davenport](https://www.researchgate.net/profile/Danielle-Davenport-2), University of Queensland  
#### [Hanny Rivera, PhD](https://www2.whoi.edu/staff/hrivera/), Woods Hole Oceanographic Institute  
#### Jecy Klinkam, College of William and Mary  
#### [Joe McGirr, PhD](https://joemcgirr.github.io/), UC-Davis 
#### Kaitlin Macaranas, CSU-Bakersfield 
#### Megan Guidry, University of Rhode Island
#### Natalie Ameral, University of Rhode Island & RI Dept. of Environmental Management 
#### [Sara Schaal](https://schaals.wixsite.com/smschaal), Northeastern University 
#### [Sara Wuitchik, PhD](https://sjswuitchik.weebly.com/), Harvard University

>>>>

Everyone is welcome to join! All seminars will be recorded and available on this website.

@@

| Date        | Topic       | Panelists     |
| :---        | :---        | :---          |
| May 7         | GBS/RADseq genotyping pipelines     | [Melanie LaCava](https://melanielacava.weebly.com/), [Alicia Mastretta-Yanes](http://mastrettayanes-lab.org/), [Isaac Overcast](https://isaacovercast.github.io/), [Jon Puritz](https://www.marineevoeco.com/)   |
| May 21       |  WGS genotyping (low and high coverage)     | [Jeffrey Good](http://www.thegoodlab.org/), [Mikhail "Misha" Matz](https://matzlab.weebly.com/), [Noah Reid](http://nreid.github.io/), [Tim Sackton](https://scholar.harvard.edu/tsackton), [Nina Overgaard Therkildsen](https://www.therkildsenlab.com/) |
| June 4       |  Population genomic analyses and filtering data     | [Zach Gompert](https://gompertlab.com/), [Morgan Kelly](http://www.morgankelly.biology.lsu.edu/), [Katie Lotterhos](https://sites.google.com/site/katielotterhos/home), [Jeff Ross-Ibarra](https://rilab.ucdavis.edu/) |
| June 18       |  Functional Genomics (RNAseq)     | [Ana Conesa](http://conesalab.org/), [Joanna Kelley](https://labs.wsu.edu/genomes/), TBD|

# Reproducibility in Marine Genomics  
The working group is also currently hosting three undergraduate research interns with funding from the [RCN-ECS](https://rcn-ecs.github.io/). These interns are part of a sub-committee conducting a literature survey to characterize trends in data availability, code accessibility, and methods reproducibility in papers that use genomics to study adaptation in marine systems. The results of this survey will be shared in a peer-reviewed article, along with guidance to improve the state of reproducibility in the field.

# Working Group Members

#### [Katherine Silliman, PhD](https://ksilliman.weebly.com/), Auburn University - kes0132[at]auburn.edu
#### [Sam Bogan](http://www.hofmannlab.com/sam-bogan.html), UC-Santa Barbara -snbogan[at]ucsb.edu
#### [Alan Downey-Wall](https://cos.northeastern.edu/people/alan-downey-wall/), Northeastern University 
#### Chris Mantegna, University of Washington  
#### [Danielle Davenport](https://www.researchgate.net/profile/Danielle-Davenport-2), University of Queensland  
#### [Hanny Rivera, PhD](https://www2.whoi.edu/staff/hrivera/), Woods Hole Oceanographic Institute  
#### Jecy Klinkam, College of William and Mary  
#### [Joanna Griffiths, PhD](https://joannasgriffiths.wordpress.com/), UC-Davis
#### [Joe McGirr, PhD](https://joemcgirr.github.io/), UC-Davis 
#### Kaitlin Macaranas, CSU-Bakersfield 
#### Megan Guidry, University of Rhode Island
#### Natalie Ameral, University of Rhode Island & RI Dept. of Environmental Management  
#### Nicolas Lou, Cornell University
#### [Sara Schaal](https://schaals.wixsite.com/smschaal), Northeastern University 
#### [Sara Wuitchik, PhD](https://sjswuitchik.weebly.com/), Harvard University
